### 2021-04-16 doc/manuscript/Dow_SI.Rmd
add leaf phenology to Table S3

```{r mean_growth_parameters_table,  eval=TRUE, echo=FALSE, warning=FALSE}
library(knitr)
library(kableExtra)
mean_growth_parameters <- read.csv("tables_figures/mean_growth_parameters.csv",  col.names = c("", "ring","diffuse","ring", "diffuse"), stringsAsFactors = FALSE, check.names = FALSE)
kable(mean_growth_parameters, caption = "Summary of parameters describing the phenology and rate of growth for ring- and diffuse- porous species at SCBI and Harvard Forest. ",  format = "latex", booktabs = TRUE,  escape = F) %>%
add_header_above(c(" ",  "SCBI" = 2, "Harvard Forest"=2 )) %>%
    column_spec(1, width = "4cm") %>%
kable_styling(latex_options = c("scale_down", "hold_position"), protect_latex = T) 
```

>>>>

```{r mean_growth_parameters_table,  eval=TRUE, echo=FALSE, warning=FALSE}
library(knitr)
library(kableExtra)
mean_growth_parameters <- read.csv("tables_figures/mean_growth_parameters.csv",  col.names = c("", "ring","diffuse","ring", "diffuse"), stringsAsFactors = FALSE, check.names = FALSE)
kable(mean_growth_parameters, caption = "Summary of parameters describing the phenology and rate of growth for ring- and diffuse- porous species at SCBI and Harvard Forest. ",  format = "latex", booktabs = TRUE,  escape = F) %>%
add_header_above(c(" ",  "SCBI" = 2, "Harvard Forest"=2 )) %>%
    column_spec(1, width = "4cm") %>%
     pack_rows("Stem Growth", 1, 8, latex_gap_space = "1em", colnum = 4, hline_before = FALSE) %>%
    pack_rows("Leaf Phenology (ecosystem level)", 9, 12, latex_gap_space = "1em", colnum = 4, hline_before = FALSE) %>%
    #add_indent(9:12)
kable_styling(latex_options = c("scale_down", "hold_position"), protect_latex = T) 
```
